Validating FF-Replan vs.\@ a State-Of-The-Art Probabilistic Planner in Translated Real World Domains

### 2014-03-30 FinalPaper/paper.tex
first part of domains

\section{Domain Descriptions}

\subsection{IPPC-2011 Domains}

@@

\subsection{Gourmand}

@@

\subsection{Reverse Iterative Deepening for Finite-Horizon MDPs with Large Branching Factors (2012)~\cite{kolobov2012glutton}}
The IPPC-2011 introduces more realistic MDPs to accommodate real-world systems with large branching factors cause by \emph{natural dynamics} and a limited time for the planner to come up with a policy. For this reason planners needed to be scalable and sensitive to the expected reward maximization. Glutton introduces an off-line algorithm based on LR\textsuperscript{2}TDP and relies on the fact that a successful policy can be produced by solving an MDP $M(H)$ for a smaller horizon $h$. Incrementally solving the sequence $M(1)$, $M(2)$ forms the basis of LR\textsuperscript{2}TDP\@. By iterating on the distance from the horizon, data can be reused (and is stored in the cache until the hash-table is full). The max-reward heuristic finds the largest horizon value $h'$ for which already a heuristic value $V$ is estimated. The  computation time remains much lower because it runs quickly into states that converged while solving $M(h-1)$. The max-reward computation relies on knowing the maximum $R_{max}$ any action can yield in any state or an upper bound on it.

\subsection{LRTDP vs. UCT for Online Probabilistic Planning\cite{kolobov2012gourmand}}
During IPPC-2011 1 out of 5 planners used a LRTDP-based system and managed to outperform three other planners using the dominant algorithm for probabilistic planning: UCT. This caused to wonder whether LRTDP planners could outperform UCT based systems.  UCT forces an expert to guess a non-shortsighted lookahead value for which it should be able to converge on encountered states. Choosing this value can have very bad consequences and its existence causes the UCT to require some input, taking away from its autonomicity. At the IPPC-2011 GLUTTON was an offline LRTDP based planner that came second. As PROST employed UCT in an online manner, GOURMAND is an online adaptation of the GLUTTON algorithm to test whether LRTDP performs better if it is employed online.

>>>>

\subsection{Gourmand}
The IPPC-2011 introduces more realistic MDPs to accommodate real-world systems with large branching factors cause by \emph{natural dynamics} and a limited time for the planner to come up with a policy. For this reason planners needed to be scalable and sensitive to the expected reward maximization. Glutton introduces an off-line algorithm based on LR\textsuperscript{2}TDP and relies on the fact that a successful policy can be produced by solving an MDP $M(H)$ for a smaller horizon $h$. Incrementally solving the sequence $M(1)$, $M(2)$ forms the basis of LR\textsuperscript{2}TDP\@. By iterating on the distance from the horizon, data can be reused (and is stored in the cache until the hash-table is full). The max-reward heuristic finds the largest horizon value $h'$ for which already a heuristic value $V$ is estimated. The  computation time remains much lower because it runs quickly into states that converged while solving $M(h-1)$. The max-reward computation relies on knowing the maximum $R_{max}$ any action can yield in any state or an upper bound on it.

During IPPC-2011 1 out of 5 planners used a LRTDP-based system and managed to outperform three other planners using the dominant algorithm for probabilistic planning: UCT. This caused to wonder whether LRTDP planners could outperform UCT based systems.  UCT forces an expert to guess a non-shortsighted lookahead value for which it should be able to converge on encountered states. Choosing this value can have very bad consequences and its existence causes the UCT to require some input, taking away from its autonomicity. At the IPPC-2011 GLUTTON was an offline LRTDP based planner that came second. As PROST employed UCT in an online manner, GOURMAND is an online adaptation of the GLUTTON algorithm to test whether LRTDP performs better if it is employed online.

\section{Domain Descriptions}
Following the theoretical comparison of probabilistic planning and replanning techniques by Little and Thi\'ebauw, a baseline test for \emph{probabilistically interesting} domains is proposed. Problems that fail this test were deemed to be classical planning problems in disguise, favouring the use of replanners \cite{little2007probvsreplan}. This section describes interesting domains in which either FF-Replan or Gourmand prevailed during the International Probabilistic Planning Compeitions. These domains are evaluated for how well they portray real-world scenarios. The domains we deem most interesting for the purpose of this paper are adjusted to match their real-world scenario. Little et all's baseline test helps us to predict which planner would perform well on these domains. We will then conclude our evaluation by comparing these results to the result of our experiments described in Section \ref{sec:experiment}.

\subsection{IPPC-2011 Domains}
The competitor FF-Replan \cite{FFReplan} kindly remembered the committee of the IPPC-04 that problems containing no dead ends and action costs are fairly easy to solve without much handling of uncertainty. The baseline test of Little et. all evaluated the competition problems of the IPPC described in PPDDL to correct the possible inaccurate perception of replanners vs.\@ probabilistic planners. IPPC-2011 responded by introducing more realistic MDPs and evluation criteria: finite-horizon MDPs evaluated on the expected reward of the created policies.

GOURMAND vastly outperformed IPPC-11 UCT-based probabilistic track winner PROST by far on goal-oriented domains Navigation and Crossing Traffic \cite{kolobov2012gourmand}. Prost however midly outperforms GOURMAND on the Game of Life, Sysadmin and the Traffic domain as UCT does not need to perform expensive Bellman Backups on these domains that include large branching factors.

\subsubsection{Navigation domain}

\subsubsection{Traffic domain}

@@

@@
